Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-08-12 Multiresolution_framework/ltx/manuscript.tex
minor edit

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ \parham{is an independent and identically distributed (i.i.d.)} Gaussian white noise process and the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix. The observation kernel models the pickup range of the electrical fields of the brain. The lead field parameters are not included in the observation equation as the intracranial recordings are considered here. \parham{The lead field parameters incorporate all the information about the head model, and must be accounted for inverse solutions when scalp electrodes are considered \cite{Jirsa2007}.} 
\section{MRA of the IDE in State-Space}
The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field. Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models. The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.

>>>>

The observation equation describing the intracranial electrophysiological recordings is given by
\begin{equation}\label{eq:ObservationEquation}
	y_t(\mathbf{r}_{n_y}) = \int_{\Omega} { m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right) v_t\left(\mathbf{r}'\right) \, \mathrm{d}\mathbf{r}'} + \epsilon_t(\mathbf{r}_{n_y}), 
\end{equation}
where $m\left(\mathbf{r}_{n_y}-\mathbf{r}'\right)$ is the observation kernel at location $\mathbf{r}_{n_y}$ and  $\boldsymbol{\epsilon}_{t}\sim \mathcal{N}\left(\mathbf{0},\mathbf{\Sigma}_{\epsilon}\right)$ \parham{is an independent and identically distributed (i.i.d.)} Gaussian white noise process with the covariance matrix $\mathbf{\Sigma}_{\epsilon}=\sigma^2_{\epsilon}\mathbf I_{n_y}$, where $\mathbf I$ denotes the identity matrix. The observation kernel models the pickup range of the electrical fields of the brain. The lead field parameters are not included in the observation equation as the intracranial recordings are considered here. \parham{The lead field parameters incorporate all the information about the head model, and must be accounted for inverse solutions when scalp electrodes are considered \cite{Jirsa2007}.} 
\section{MRA of the IDE in State-Space}
The purpose of forming the multi-resolution approximation (MRA) of the integro-difference equation (IDE) is to form a multi-resolution finite-dimensional state-space model that best captures the spatiotemporal characteristics of the neural field. Given such a model, it is then possible to perform state and parameter estimation in an efficient and robust manner, thus allowing for subject-specific models. The goal of this section is to demonstrate how to formulate a state-space model in a canonical form such that standard algorithms may be applied to estimate the multi-resolution connectivity structure.
